\newcommand{\aw}{\underline{Akifumi Wachi}}
\section{Publications}

\begin{enumerate}

\item
Mikoto Kudo, Takumi Tanabe, \aw, Youhei Akimoto
``Sample-Efficient Hypergradient Estimation for Decentralized Bi-Level Reinforcement Learning''
International Conference on Automated Planning and Scheduling (ICAPS), 2026.

\item 
Shigeki Kusaka, Keita Saito, Mikoto Kudo, Takumi Tanabe, \aw, Youhei Akimoto,
``Cost-Minimized Label-Flipping Poisoning Attack to LLM Alignment''
AAAI Conference on Artificial Intelligence (AAAI), 2025.

\item 
\aw, Kohei Miyaguchi, Takumi Tanabe, Rei Sato, Youhei Akimoto,
``A Provable Approach for End-to-End Safe Reinforcement Learning''
Neural Information Processing Systems (NeurIPS), 2025.

\item
Runze Yan, Xun Shen, \aw, Kohei Miyaguchi, Takumi Tanabe, Rei Sato, Youhei Akimoto, Sebastien Gros, Anni Zhao, Xiao Hu,
``Offline Guarded Safe Reinforcement Learning for Medical Treatment Optimization Strategies''
Neural Information Processing Systems (NeurIPS), 2025. (Spotlight)

\item 
Kensuke Tatematsu, \aw,
``Target Return Optimizer for Multi-Game Decision Transformer''
Asian Conference on Machine Learning (ACML), 2025.

\item 
Kazumune Hashimoto, Yuga Onoue, \aw, Xun Shen,
``Learning-Based Event-Triggered MPC With Gaussian Processes Under Terminal Constraints''
IEEE Transactions on Cybernetics, 2025.

\item
\aw, Thien Q. Tran, Rei Sato, Takumi Tanabe, Youhei Akimoto,
``Stepwise Alignment for Constrained Language Model Policy Optimizations''
Neural Information Processing Systems (NeurIPS), 2024.

\item
Xun Shen, Shuo Jiang, \aw, Kazumune Hashimoto, Sebastien Gros,
``Flipping-based Policy for Chance-Constrained Markov Decision Processes''
Neural Information Processing Systems (NeurIPS), 2024.


\item 
\aw, Xun Shen, Yanan Sui,
``A Survey of Constraint Formulations in Safe Reinforcement Learning''
International Joint Conference on Artificial Intelligence (IJCAI), Survey Track, 2024.

\item 
\aw, Wataru Hashimoto, Kazumune Hashimoto,
``Long-term Safe Reinforcement Learning with Binary Feedback''
AAAI Conference on Artificial Intelligence (AAAI), 2024.

\item
Xun Shen, \aw, Wataru Hashimoto, Kazumune Hashimoto, Shigemasa Takai
``Safe Reinforcement Learning Using Model Predictive Control with Probabilistic Control Barrier Function''
American Control Conference (ACC), 2024.

\item 
\aw, Wataru Hashimoto, Xun Shen, Kazumune Hashimoto,
``Safe Exploration in Reinforcement Learning: A Generalized Formulation and Algorithms''
Neural Information Processing Systems (NeurIPS), 2023.

\item
\aw, Yunyue Wei, Yanan Sui,
``Safe Policy Optimization with Local Generalized Linear Function Approximations''
Neural Information Processing Systems (NeurIPS), 2021.

\item
Ran Iwamoto, Ryosuke Kohita, \aw,
``Polar Embedding''
The SIGNLL Conference on Computational Natural Language Learning (CoNLL), 2021.

\item 
Daiki Kimura, Masaki Ono, Subhajit Chaudhury, Ryosuke Kohita, \aw, Don Joven Agravante, Michiaki Tatsubori, Asim Munawar, Alexander Gray,
``Neuro-Symbolic Reinforcement Learning with First-Order Logic''
Empirical Methods in Natural Language Processing (EMNLP), Short paper, 2021.

\item 
Ryosuke Kohita, \aw, Daiki Kimura, Subhajit Chaudhury, Michiaki Tatsubori, Asim Munawar,
``Language-based General Action Template for Reinforcement Learning Agents''
Association for Computational Linguistics (ACL), Findings, 2021.

% EMNLP 2020
\item Ryosuke Kohita, \aw, Yang Zhao, Ryuki Tachibana,
"Q-learning with Language Model for Edit-based Unsupervised Summarization"
Empirical Methods in Natural Language Processing (EMNLP), 2020 
%(Acceptance rate: 22.4 \%)

% ICML 2020
\item
\underline{A. Wachi}, Y. Sui, "Safe Reinforcement Learning in Constrained Markov Decision Processes", International Conference on Machine Learning (ICML), 2020

% IJCAI 2019
\item
\underline{A. Wachi}, "Failure-Scenario Maker for Rule-based Agent using Multi-agent Adversarial Reinforcement Learning and its Application to Autonomous Driving", International Joint Conference on Artificial Intelligence (IJCAI), 2019 


% AAAI 2018
\item
\underline{A. Wachi}, Y. Sui, Y. Yue, M. Ono, "Safe Exploration and Optimization of Constrained MDPs using Gaussian Processes", AAAI Conference on Artificial Intelligence (AAAI), 2018


% Acta Astronautica
\item R. Sakagami, R. Takahashi, \underline{A. Wachi}, Y. Koshiro, H. Maezawa, Y. Kasai, S. Nakasuka, "Integral Design Method for Simple and Small Mars Lander System Using Membrane Aeroshell", Acta Astronautica.
% AIAA Space
\item \underline{A. Wachi}, R. Takahashi, R. Sakagami, Y. Koshiro, Y. Kasai, S. Nakasuka, "Feasibility Study for Mars Landing with Small Space Probe", AIAA SPACE and Astronautics Forum and Exposition (2017 AIAA SPACE Forum), 2017.

% ISTS (A. Wachi)
\item \underline{A. Wachi}, "Low-Thrust Trajectory Design to Improve Overall Mission Success Probability Incorporating Target Changes in Case of Engine Failures", 31st International Symposium on Space Technology and Science (ISTS), 2017. {\bf Nominated to Best Student Paper Award: First Prize (General Chairperson Award)}
% IFAC
\item \underline{A. Wachi}, N. Ozaki, S. Nakasuka, "Fault-Tolerant Low-Thrust Trajectory Design with Backups for Multiple Targets", 20th IFAC Symposium on Automatic Control in Aerospace (ACA), 2016. {\bf Nominated to the Best Student Paper Award: First Prize.}
\end{enumerate}


\section{Patents}

I have over 10 filed patents which can be found here:
\begin{itemize}
    \item \url{https://patents.justia.com/search?q=akifumi+wachi}
\end{itemize}